The Impact of Interview Disruptions on Data Quality in Social Surveys

### 2024-12-01 paper/paper.qmd
update paper

@@

@@

confusion_matrix <- matrix(c(41, 36, 129, 3970), nrow = 2, byrow = TRUE,
                           dimnames = list("Prediction" = c("Not_understood", "Understood"),
                                           "Reference" = c("Not_understood", "Understood")))

>>>>

## Alternative model
```{r}
first_model1 <-
  readRDS(file = here::here("models/glmmodel.rds"))
summary <- summary(first_model1)
analysis_data_train <- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
analysis_data_test <- read_parquet(here::here("data/02-analysis_data/test_data.parquet"))
factor_vars <- c("interview_conduct_method", "partner_interference", "child_interference",
                 "parent_interference", "relative_interference", "non_relative_interference",
                 "country", "interviewer_gender", "question_clarification", "respondent_reluctant",
                 "respondent_tried_best")

# Predict probabilities and convert predicted_class to "Understood" and "Not_understood"
predicted_prob <- predict(first_model1, newdata = analysis_data_test, type = "response")
analysis_data_test$predicted_class <- ifelse(predicted_prob > 0.5, "Understood", "Not_understood")

confusion_matrix1 <- confusionMatrix(
  analysis_data_test$predicted_class,
  analysis_data_test$respondent_understood_binary
)

confusion_matrix1
```

@@

confusion_matrix
confusion_matrix <- matrix(c(41, 36, 129, 3970), nrow = 2, byrow = TRUE,
                           dimnames = list("Prediction" = c("Not_understood", "Understood"),
                                           "Reference" = c("Not_understood", "Understood")))

@@
